Idea Development

### 2024-11-11 posts/Abortion/abortion.qmd
Abortion papers

>>>>

### References

-   Ozer et al. - 2023 - Digital Multisided Platforms and Women’s Health An Empirical Analysis of Peer-to-Peer Lending and Abortion Rates

    <iframe src="PDF/Ozer et al. - 2023 - Digital Multisided Platforms and Women’s Health An Empirical Analysis of Peer-to-Peer Lending and A.pdf" style="width:100%; height:1500px;" frameborder="0">

    </iframe>

-   Augustine and Piazza - 2022 - Category Evolution Under Conditions of Stigma The Segregation of Abortion Provision into Specialist Clinics in the United States

    <iframe src="PDF/Augustine and Piazza - 2022 - Category Evolution Under Conditions of Stigma The Segregation of Abortion Provision into Specialist.pdf" style="width:100%; height:1500px;" frameborder="0">

    </iframe>

-   Thomadsen et al. - 2023 - The Impact of a Supreme Court Decision on the Preferences of Americans Regarding Abortion Policy

    <iframe src="PDF/Thomadsen et al. - 2023 - The Impact of a Supreme Court Decision on the Preferences of Americans Regarding Abortion Policy.pdf" style="width:100%; height:1500px;" frameborder="0">

    </iframe>
